\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-25 papers/jss/article.Rnw
Use listings package to add line numbers so we can explain an example in section 7 better per referee #1 feedback.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@905 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[article]{jss}
\usepackage{booktabs}
\usepackage[toc,page]{appendix}

@@

% TODO(mstokely): commentd out per referee feedback, but see if this is
% covered in the package documentation well.
%
%\code{serialize} can also be called in a more traditional
%object oriented fashion using the dollar operator.
%
%<<>>=
%p$serialize(tf1)
%con <- file(tf2, open = "wb")
%p$serialize(con)
%close(con)
%@
%
%Here, we first serialize to a file \code{tf1} before we serialize to a binary
%connection to file \code{tf2}.

@@

\begin{itemize}
\item The functional dispatch mechanism of the the form
  \verb|method(object, arguments)| (common to \proglang{R}), and
\item The traditional object oriented notation
  \verb|object$method(arguments)|.
\end{itemize}

@@

The Protocol Buffer can then be read into \proglang{R} and converted to a native
\proglang{R} histogram object for plotting. Here, the schema is read first,
then the (serialized) histogram is read into the variable \code{hist} which
is then converted a histogram object which is display as a plot.

\begin{Code}
library("RProtoBuf")
library("HistogramTools")

readProtoFiles(package="HistogramTools")

hist <- HistogramTools.HistogramState$read("/tmp/hist.pb")
hist
[1] "message of type 'HistogramTools.HistogramState' with 3 fields set"

plot(as.histogram(hist))
\end{Code}

\begin{center}
<<echo=FALSE,fig=TRUE,width=8,height=4>>=
require(RProtoBuf)
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("hist.pb")
plot(as.histogram(hist))
@
\end{center}

>>>>

\documentclass[article]{jss}
\usepackage{booktabs}
\usepackage{listings}
\usepackage[toc,page]{appendix}

@@

% TODO(mstokely): commentd out per referee feedback, but see if this is
% covered in the package documentation well.
%
%\code{serialize} can also be called in a more traditional
%object-oriented fashion using the dollar operator.
%
%<<>>=
%p$serialize(tf1)
%con <- file(tf2, open = "wb")
%p$serialize(con)
%close(con)
%@
%
%Here, we first serialize to a file \code{tf1} before we serialize to a binary
%connection to file \code{tf2}.

@@

\begin{itemize}
\item The functional dispatch mechanism of the the form
  \verb|method(object, arguments)| (common to \proglang{R}), and
\item The message passing object-oriented notation of the form
  \verb|object$method(arguments)|.
\end{itemize}

@@

The Protocol Buffer created from this \proglang{Python} script can then be read into \proglang{R} and converted to a native
\proglang{R} histogram object for plotting.  Line~1 in the listing below attaches the \pkg{HistogramTools} package which imports \pkg{RProtoBuf}.  Line~2 then reads all of the \code{.proto} descriptor definitions provided by \pkg{HistogramTools} and adds them to the environment as described in Section~\ref{sec:rprotobuf-basic}.  Line~3 parses the serialized protocol buffer using the \code{HistogramTools.HistogramState} schema.  Line~8 converts the protocol buffer representation of the histogram to a native \proglang{R} histogram object with \code{as.histogram} and passes the result to \code{plot}.

% Here, the schema is read first,
%then the (serialized) histogram is read into the variable \code{hist} which
%is then converted a histogram object which is display as a plot.

\lstdefinelanguage{jss}
  {sensitive=false,
   morecomment=[l]{R>}}

\lstset{language=jss, basicstyle=\ttfamily, numbers=left, numberstyle=\tiny, stepnumber=2, numbersep=5pt, columns=fullflexible, keepspaces=true, showstringspaces=false, commentstyle=\textsl}
%\begin{Code}
\begin{lstlisting}
R> library("HistogramTools")
R> readProtoFiles(package="HistogramTools")
R> hist <- HistogramTools.HistogramState$read("/tmp/hist.pb")
R> hist

[1] "message of type 'HistogramTools.HistogramState' with 3 fields set"

R> plot(as.histogram(hist))
\end{lstlisting}
%\end{Code}

\begin{center}
<<echo=FALSE,fig=TRUE,width=8,height=4>>=
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("hist.pb")
plot(as.histogram(hist))
@
\end{center}
